Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-24 jessie-writeup/jessie-writeup.tex
Updates to Jessie's writeup

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets, and not a function.
\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}

@@

\begin{notation}
  Consider two labeled properties $\Gamma' : \P \toto \R$ and $\Gamma : \P \toto \R$.
  We say $\Gamma' \preceq \Gamma$ if removing reports from $\Gamma$ yields $\Gamma'$, that is, if $\Gamma' = \Gamma \cap \varphi(\R')$ for some $\varphi(\R') \subseteq \R$.
  \jessiet{Changed $\R' \subseteq \R$ to $\varphi(\R') \subseteq \R$.}
\end{notation}

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.  JF: you're right... shoot}
  \jessie{Should be equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma$ be a nondegenerate elicitable property with a finite set of \jessie{full-dimensional} level sets \jessie{$\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$}.
	There exists a nondegenerate, nonredundant property $\Gamma'$ such that $\Gamma' \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable a.e.}\raft{Confused by BR}

	To start, construct $\R' \subseteq \R := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \}$.
	Clearly, $\R'$ is finite (and nonempty since finitely many level sets implies at least one must have nonempty interior).
	Defining the property $\Gamma' = \Gamma\cap \R'$, we see that $\Gamma' \preceq \Gamma$.
	We want to show that the constructed $\Gamma'$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \R$ such that $r \in \Gamma(p)$.
	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
	Since level sets are closed, for distributions on the boundary of a level set, the optimal report $r \in \R'$ is still an optimal report, thus there is at least one report $r \in \R'$ such that $r \in \Gamma(p)$ for all $p \in \P$, so $\Gamma'$ is nondegenerate.

@@

	Now to show $\Gamma'$ is nonredundant.
	For contradiction, suppose $\Gamma'$ is redundant.
	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$ or $\Gamma'_{r_1} = \Gamma'_{r_2}$.

	First, suppose $\Gamma'_{r_1} = \Gamma'_{r_2}$.
	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
	\jessie{Need source: Gneiting Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
	Then $\Gamma'(p) = \partial G(p) \implies |\Gamma'(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\Gamma'_{r_1}$ and $\Gamma'_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\Gamma'_{r_1} = \Gamma'_{r_2}$.

%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?

	Otherwise suppose $\Gamma'_{r_1} \subsetneq \Gamma'_{r_2}$.
	As $\Gamma'_{r_1}$ is full-dimensional, so is $\Gamma'_{r_1} \cap \Gamma'_{r_2} = \Gamma'_{r_1}$.
	Again, since we know that $|\Gamma'(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
	Therefore, $\Gamma'$ is nonredundant.

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property \jessie{with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$?}.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\Gamma' \preceq \Gamma$, we have $\strip(\Gamma') = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

@@

	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$.
	Intuitively, we see this because both $\Gamma'$ and $\tilde{\Gamma}$ are restrictions of the property $\Gamma$, so every level set of a restricted property must be a superset of or equal to a level set of $\Gamma$.
%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.

@@

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\Gamma' \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\Gamma' = \Gamma\cap \R'$.
	For each $\theta \in \trim(\Gamma) = \strip(\Gamma)$, there must be a report $r \in \R'$ such that $\theta = \Gamma'_r$.
	By construction, $r \in \R' \implies \inter{\Gamma'_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

	Therefore, every level set $\theta \in \trim(\Gamma)$ is full-dimensional.

@@

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the elicitable property $\Gamma$ embed the nondegenerate property $\gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{conjecture}

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $p \in \Gamma_r \implies \exists r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

	Consider $p \in \Gamma_r$.
	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r' = \varphi(r) \in \gamma(p)$ and $r' \in \R'$.
	We then know that $p \in \gamma_{r'}$.
	Now suppose $q \in \Gamma_r$ and $\varphi(r) = r_1 \neq r'$.
	Therefore, $q \not \in \gamma_{r'}$, which contradicts the the fact that $\Gamma$ embeds $\gamma$.
	Thus, there must be an $r' \in \R'$ so that $p \in \gamma_{r'}$ for all $p \in \Gamma_r$.

@@

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  Let $\Gamma:\P\toto\R$ be a non-degenerate elicitable property.

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ such that there is an injection $\varphi:\R'\to\R$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$)
  \item There is a finite set of full dimensional level sets of $\Gamma$ that union to $\P$.
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.

@@

\begin{proof}
\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.}
We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.

@@

\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
We want to show that $\Gamma$ embeds this property $\gamma$.
First, we know $\gamma$ is nondegenerate and finite by construction.

Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, $\R$, then $\card(\R')) \leq \card(\R)$ \jessie{$?= \card(\reals^d)$... again assuming $\R$ is a \emph{convex} subset of $\reals^d$}, there is an injection $\varphi : \R' \to \R$ from Folland Section 0.

Consider some $r \in \gamma(p)$.
Since there is an injection $\varphi$ from $\R' \to \R$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.

Now consider $\trim(\Gamma) = \strip(\gamma)$.
Therefore, for every level set $\theta\in\trim(\Gamma)$, there is a corresponding level set $\theta' \in \strip(\gamma)$ so that $\theta = \theta'$.

For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.

Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.

Therefore, if $\trim(\Gamma)$ is finite, then $\Gamma$ embeds the finite, nondegenerate property $\gamma$ such that $\trim(\Gamma) = \strip(\gamma)$ .
Thus, $5 \implies 1$.

@@

\item [$6 \implies 2$]
Since $\Gamma$ is non degenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the  (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.

\item [$2 \implies 3$]
We know that (a.) is satisfied by assumption.
Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere.
In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.

>>>>

A set $\Theta \subseteq 2^{\Delta(\Y)}$ is an unlabeled property, and finite if $|\Theta| < \infty$.
Observe that $\Theta$ is a set of level sets, and not a function.
%\raft{Careful: $\Theta$ does not need to divide anything; $\Theta = \{\emptyset\}$ is technically an unlabeled (degenerate) property JF: Changed}

@@

\begin{notation}
\jessiet{TODO: REVISIT THIS.  See Notation 3}
  Consider two labeled properties $\gamma : \P \toto \R'$ and $\Gamma : \P \toto \R$.
  We say $\gamma \preceq \Gamma$ if removing reports from $\Gamma$ yields $\gamma$.
  That is, if $\gamma = \Gamma \cap \varphi(\R')$ for some injection $\varphi : \R' \to \R$.
  Note that $\varphi(\R') \subseteq \R$.
  %\jessie{Technically, if labeled, we also want a bijection $\phi: \R' \to \varphi(\R)$ so that $\phi(\gamma) = \Gamma \cap \varphi(\R')$, where $\phi = \varphi$ restricted to the range of $\varphi$.  We would then say $\gamma \preceq \Gamma$ if $\phi(\gamma) = \Gamma \cap \varphi(\R)$...?}
\end{notation}

\begin{notation}
\jessie{Attempt 2 of the above}
Let $\gamma: \P \toto\R'$ and $\Gamma: \P \toto\R$.
We say $\gamma \preceq \Gamma$ if there exists an injection $\varphi: \R' \to \R$ so that for all $p \in\P$, we have $\varphi(\gamma(p)) \in \Gamma(p)$. 
%\jessie{The $\cap \varphi(\R')$ isn't necessary anymore, right...?}
\end{notation}

\begin{definition}
\jessiet{Not sure we need this, but I feel like it might be useful in the future for showing uniqueness up to a relabeling.}
Let $\gamma$ and $\zeta$ be set-valued properties.
We say $\gamma~\approx~\zeta$ if $\strip(\gamma)~=~\strip(\zeta)$.
\end{definition}

\begin{conjecture}
Consider a nondegenerate $\gamma:\P \toto\R'$ and $\Gamma: \P \toto\R$.
For any bijection $\phi: \R' \to \bar \R$ and property $\zeta : p \mapsto \phi(\gamma(p))$, we observe that $\gamma \preceq \Gamma \iff \zeta \preceq \Gamma$.
\end{conjecture}
\begin{proof}
Assume $\gamma \preceq \Gamma$.
Then there is an injection $\varphi: \R' \to \R$ so that $\varphi(\gamma(p)) \in \Gamma(p)$ for all $p\in \P$.
Consider $\bar \R = \phi(\R')$, and define the injection $\bar \varphi: \bar \R \to \R$ so that $\bar \varphi: \phi(r) \mapsto \varphi(r)$.

Consider $\strip(\gamma)  = \{\Gamma_r : r \in \R' \} = \{ \Gamma_{r} : \phi(r) \in \bar \R \} = \strip(\zeta)$. 
Therefore, $\gamma \approx \zeta$.
Since $\zeta(p) = \phi(\gamma(p))$, we know that $\bar \varphi (\zeta(p)) = \varphi(\gamma(p))$.
%Since $\strip(\gamma) = \strip(\zeta)$, we then know that for all $p \in \P$, that $p \in \gamma_r \iff p \in \zeta_{\phi(r)}$, and therefore $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar \varphi(\zeta(p)) \in \Gamma(p)$.

Thus, $\varphi(\gamma(p)) \in \Gamma(p) \iff \bar{\varphi}(\zeta(p)) \in \Gamma(p)$, so we conclude $\zeta \preceq \Gamma$.
The other direction follows with the same logic, using $\phi^{-1}$.
\end{proof}

In this case, we say $\zeta$ is a relabeling of $\gamma$.

@@

\begin{definition}\label{def:unlabeled-nonredundant}
  An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
%  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.  JF: you're right... shoot}
  \jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

Other notes before starting:
\begin{itemize}
\item (Assuming the metric space is $(\Delta(\Y), \rho)$, where $\rho$ is Euclidean distance, although I don't think the choice of metric matters?).
We just use this looking at interiors of level sets.
\item Using generalized Lebesgue measure on $\P \subset \reals^{|\Delta(\Y)|-1}$
\item The interior of a level set $X_r$ is defined as $\inter{X_r} = \{p \in X_r: \epsilon > 0,  \forall q \in B(\epsilon,p), r \in \argmin_r \E_q L(r,Y)\}$
\item Define the boundary of the closed set $X$ by $bd(X) := X \setminus \inter{X}$.
\item A convex level set $\theta$ is \emph{full-dimensional} if it has nonempty interior. %% old: $dim(\aff(\theta)) = dim(\P)$. 
%Equivalently, $\theta$ is full-dimensional if there are distributions $p_1, p_2, \ldots, p_n \in \theta$ so that $p_1, \ldots, p_n$ are affinely independent.
%\raft{Careful; I think you need convexity here.  Probably you want to define full-dimensional as having nonempty interior, and prove this as a consequence of convexity.}
%\jessiet{What is the formal, ``universal'' definition of full-dimensional, if one exists?}
%\item A full-dimensional level set has non-empty interior.
\end{itemize}

@@

\begin{conjecture}\label{conj:gam-prime-exists}
	Let $\Gamma:\P \toto \reals^d$ be a nondegenerate elicitable property with a finite set of full-dimensional level sets $\Theta$ so that $\bigcup_{\theta \in \Theta}\theta = \P$.
	There exists a nondegenerate, nonredundant property $\gamma$ such that $\gamma \preceq \Gamma$. 
\end{conjecture}
\begin{proof}
\emph{Assumptions used: Finite level sets, elicitability implies convex score $G$, i.e. differentiable 	a.e.}

	Construct $\R := \{ r \in \reals^d : \exists p \in \P \text{ so that } r \in \Gamma(p) \}$, which is union of the elements in the range of $\Gamma$.

	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
	Observe that $\R'$ is finite and nonempty.
	Defining the property $\gamma = \Gamma\cap \varphi(\R')$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
	Removing redundant reports resolves (a.) and (b.).
	As $\Gamma$ is elicitable, we can see that (c.) cannot happen without contradicting elicitability by ... \jessie{closure of subgradient sets on the score $G$?}

	Therefore, there will be at least one $r \in \R'$ per distribution, and as level sets are closed, so $\gamma$ will still be nondegenerate.
	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

@@

%%% COMMENTED OUT 10/19/18
%%%	Now to show $\gamma$ is nonredundant.
%%%	For contradiction, suppose $\gamma$ is redundant.
%%%	Then there are $r_1, r_2 \in \R'$ with $r_1 \neq r_2$ with full dimensional level sets $\Gamma_{r_1}$ and $\Gamma_{r_2}$ so that either $\gamma_{r_1} \subsetneq \gamma_{r_2}$ or $\gamma_{r_1} = \gamma_{r_2}$.
%%%	
%%%	\jessie{Uses a fact that requires nonredundancy to show nonredundancy... change this proof.  Or think about what it's not true.}
%%%	First, suppose $\gamma_{r_1} = \gamma_{r_2}$.
%%%	We can think as the property values as labelings of the subgradient sets (denoted by $\partial$) of the the concave Bayes Risk $G(p)$.
%%%	\jessie{Need source: Gneiting/Raftery 2007\footnote{\url{https://www.stat.washington.edu/raftery/Research/PDF/Gneiting2007jasa.pdf}} or Raf/Ian 2014\footnote{\url{http://www.cs.colorado.edu/~raf/media/papers/wine-affine.pdf}}}
%%%	As $G$ is concave, it is differentiable almost everywhere, which means that $|\partial G(p)| = 1$ almost everywhere.
%%%	Then $\gamma(p) = \partial G(p) \implies |\gamma(p)| = 1$ almost everywhere, which-- along with the fact that the level sets $\gamma_{r_1}$ and $\gamma_{r_2}$ are full dimensional (and therefore have positive measure since they are convex-- see Lemma~\ref{lem:pos-measure-iff-nonempty-int}), contradicts the claim $r_1 \neq r_2$.
%%%	Thus we conclude there aren't reports $r_1, r_2 \in \R'$ so that $r_1 \neq r_2$ and $\gamma_{r_1} = \gamma_{r_2}$.
%%%	
%%%%	By construction of $\R'$, we know both $\Gamma'_{r_1}$ and  $\Gamma'_{r_2}$ are full dimensional.
%%%%	If $\Gamma'_{r_1} = \Gamma'_{r_2} = \Gamma'_{r_1} \cap \Gamma'_{r_2}$ are full dimensional, this contradicts something?
%%%	
%%%	Otherwise suppose $\gamma_{r_1} \subsetneq \gamma_{r_2}$.
%%%	As $\gamma_{r_1}$ is full-dimensional, so is $\gamma_{r_1} \cap \gamma_{r_2} = \gamma_{r_1}$.
%%%	Again, since we know that $|\gamma(p)| = 1$ almost everywhere, and as the intersection of the two level sets is full-dimensional, this again contradicts the differentiability of $G$ almost everywhere, since the intersection of the level sets has positive measure in the simplex.
%%%	Therefore, $\gamma$ is nonredundant.
%%% END COMMENTED OUT 10/19/18
\end{proof}

\begin{lemma}\label{lem:define-trim}
	Let $\Gamma$  be a nondegenerate, elicitable property with a finite set of level sets $\Theta$ so that $\cup_{\theta \in \Theta} \theta = \P$.
	There exists an unlabeled property $\Theta$ so that for all nondegenerate, nonredundant $\gamma \preceq \Gamma$, we have $\strip(\gamma) = \Theta := \text{trim}(\Gamma)$.
\end{lemma}

@@

	As $\Gamma' \preceq \Gamma$ and $\tilde \Gamma \preceq \Gamma$, then for some $r \in \tilde \R$, we then see that either $\Gamma'_{r'} \subsetneq \tilde \Gamma_r$ or $\tilde \Gamma_r \subsetneq \Gamma'_{r'}$ since both $\Gamma'$ and $\tilde \Gamma$ are restrictions of the property $\Gamma$.
%	(If the level sets are not equivalent, then the intersection $\Gamma'_{r'} \cap \tilde{\Gamma_r}$ must be lower dimensional by nonredundancy of $\Gamma'$ and $\tilde{\Gamma}$ since $\partial G$ is real-valued amost everywhere.)
	The first case contradicts nonredundancy of $\Gamma'$ and the latter contradicts nonredundancy of $\tilde \Gamma$.
	Thus, there must be some $r \in \tilde{\R}$ so that $\Gamma'_{r'} = \tilde{\Gamma_r}$, so we conclude $\Gamma'_r \in \strip(\tilde \Gamma)$.

@@

	\jessie{If we think about bijections, consider the bijection $\phi: \R' \to \tilde \R$.
	Then $\strip(\Gamma') = \{ \Gamma'_{r} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : r \in \R' \} = \{ \Gamma_{\varphi(r)} : \phi(r) \in \tilde \R \} = \{ \tilde \Gamma_{\phi(r)} : \phi(r) \in \tilde \R \} = \strip(\tilde \Gamma) $, then it's simpler to state.}

@@

	In order to understand what $\trim(\Gamma)$ is, we use the property $\gamma \preceq \Gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists}, and suppose $\R'$ is the set such that $\gamma = \Gamma\cap \varphi(\R')$.
	For each $\theta \in \trim(\Gamma) = \strip(\gamma)$, there must be a report $r \in \R'$ such that $\theta = \gamma_r = \Gamma_{\varphi(r)}$.
	By construction, $r \in \R' \implies \inter{\gamma_r} = \inter{\theta} \neq \emptyset$.
	Since $\theta$ is convex (as level sets of elicitable properties are) and has nonempty interior, then $\theta$ is full dimensional.

@@

\begin{conjecture}\label{conj:lev-sets-subsets}
	Let the elicitable property $\Gamma: \P \toto \reals^d$ embed the nondegenerate property $\gamma$.
	Then the level sets of $\Gamma$ are subsets of the level sets of $\gamma$.
\end{conjecture}

\begin{proof}
	Showing the level sets of $\Gamma$ are subsets of the level sets of $\gamma$ is to show that $\forall r \in \reals^d$ we know $p \in \Gamma_r \implies p \in \gamma_{r'}$ for some $r' \in \R'$.
    \raf{Want to say $\forall r$ $\exists r'$ $p \in \Gamma_r \implies p \in \gamma_{r'}$.}

%	Consider $p \in \Gamma_r$.
%	Then $r \in \Gamma(p)$, and since $\Gamma$ embeds $\gamma$, we know $ r = \varphi(r') \in \gamma(p)$ and $r' \in \R'$.
%	We then know that $p \in \gamma_{r'}$.
	Consider $r_1 \in \reals^d$ and $r_2 \in \R'$.
	Suppose $q \in \Gamma_{r_1}$ but $q \not \in \gamma_{r_2}$.
	There must be no $r_2 \in \R'$ so that $\varphi(r_2) = r_1$.
	Then $q \not \in \gamma_{r_2}$ contradicts the the fact that $\Gamma$ embeds $\gamma$.
	Thus, $p \in \Gamma_{r_1} \implies \exists r_2 \in \R'$ so that $p \in \gamma_{r_2}$ .

@@

\begin{proposition}\label{prop:optimal-reports-per-level-set}
  Let $\Gamma:\P\toto\reals^d$ be a non-degenerate elicitable property.

  The following are equivalent:
  \begin{enumerate}
  \item There is a nondegenerate, finite property $\gamma:\P\toto\R'$ and $\R \subseteq \reals^d$ such that there is an injection $\varphi:\R'\to\reals^d$ such that $r\in\gamma(p) \iff \varphi(r) \in \Gamma(p)$. (i.e. $\Gamma$ embeds finite $\gamma$).  
%  \jessie{Note: If $\R = \varphi(\R')$, then $\varphi': \R' \to \R$ with $\varphi': r \mapsto \varphi(r) \cap \R$ is a bijection, if we want to talk about inverses.}
  \item There is a finite set of full dimensional level sets $\Theta$ of $\Gamma$ that union to $\P$.
  \item There is a finite set $\Theta \subseteq \strip(\Gamma)$ of full-dimensional level sets, such that: (a) $\bigcup_{\theta\in\Theta} \theta = \P$%, (b) for all $\theta \in \Theta$, there exists an $r_\theta \in \R$ such that $\Gamma(p) = \{r_\theta\}$ for all $p \in \inter{\theta}$.
  \item $\strip(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite.
  \item $\trim(\Gamma)$ is finite and elicitable.

@@

\begin{proof}
%\jessie{Old: First, we show $5 \iff 4$ then proceed in a cycle to show $1 \implies 3 \implies 2 \implies 6 \implies 5 \implies 1$.
%	Also old: We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 3 \implies 4 \implies 5$.	}
We proceed in a cycle to show $5 \implies 1 \implies 6 \implies 2 \implies 4 \implies 5$.

@@

\item[$5 \implies 1$] Let $\trim(\Gamma)$ be finite.
Then there is a nondegenerate, nonredundant, finite property $\gamma: \P \to \R'$ and $\gamma \preceq \Gamma$ so that $\{ \gamma_r : r \in \R' \} = \strip(\gamma) = \trim(\Gamma)$, and we take $\gamma, \varphi$ as constructed in Conjecture~\ref{conj:gam-prime-exists}.
We want to show that $\Gamma$ embeds this property $\gamma$.
We know $\gamma$ is nondegenerate and finite by construction.

%Since we know $\card(\trim(\Gamma)) = \card(\R')$ is finite and $\trim(\Gamma)$ is a subset of the codomain of $\Gamma$, then $\card(\R')) \leq \card(\reals^d)$, so there is an injection $\varphi : \R' \to \reals^d$ \jessie{Citation if desired: from Folland Section 0.3}.
%\jessie{Let us construct $\R = \varphi(\R')$ so that $\bar \varphi: \R' \to \R$ is a bijection.}

Consider some $r \in \gamma(p)$.
Since $\varphi$ is an injection from $\R' \to \reals^d$, then $r \in \gamma(p) \implies \varphi(r) \in \varphi(\gamma(p)) \subseteq \Gamma(p) \implies \varphi(\gamma(p)) \in \Gamma(p)$.
Therefore, we are just left to show $\varphi(r) \in \Gamma(p) \implies r \in \gamma(p)$.

Consider $r \in \R'$ so that $\varphi(r) \in \Gamma(p)$.
If $r \not \in \gamma(p)$, we contradict $\varphi(\gamma(p)) \in \Gamma(p)$, so $r$ must be in $\gamma(p)$.

Thus, $\trim(\Gamma)$ finite $\implies \Gamma$ embeds $\gamma = \trim(\Gamma)$.

%If $r \not \in \R$, there is some $r' \in \R$ so that $\Gamma_r \subseteq \Gamma_{r'}$, and we show $p \in \Gamma_r \implies p \in \Gamma_{r'} \implies p \in \gamma_{\bar \varphi^{-1}(r')}$.

%For any $r \in \R$, consider the level set $\Gamma_r$, if $\Gamma_r \in \trim(\Gamma)$, then there is a corresponding $\gamma_{r'}$ so that $p \in \Gamma_r \implies p \in \gamma_{r'}$ as $\strip(\gamma) = \trim(\Gamma)$.
%
%Now, if for some $r \in \R$, we observe $\Gamma_r \not \in \trim(\Gamma)$, we know $\Gamma_r$ is not full dimensional by Conjecture~\ref{conj:trim-full-dim}.
%As level sets of elicitable properties are closed (Lemma~\ref{lem:closed-level-sets}), there is some other $\tilde r \in \R$ so that $\Gamma_{\tilde r} \in \trim(\Gamma)$ and $p \in \Gamma_r \implies p \in \Gamma_{\tilde r} \implies p \in \gamma_{r'}$ for some $r' \in \R'$ so that $\tilde r = \varphi(r')$.

@@

\item [$6 \implies 2$]
Since $\Gamma$ is nondegenerate and every $\theta \in \trim(\Gamma)$ is full dimensional (Conjecture~\ref{conj:trim-full-dim}), it is clear that the union of the (full-dimensional) level sets of $\trim(\Gamma)$ union to $\P$.

%\item [$2 \implies 3$]
%We know that (a.) is satisfied by assumption.
%Since $\Gamma$ is elicitable, the convex score $G(p)$ corresponds to the optimal report set at a distribution $p$.
%Since $G$ is convex, it is differentiable almost everywhere, so the optimal report is unique almost everywhere. \jessie{Can't say this unless $\Gamma$ is nonredundant.}
%In the interior of a convex level set has positive measure, the optimal report on the interior of each level set must then be unique.
